Cost- and Deadline-constrained Scheduling of Scientific Workflow Ensembles in IaaS Clouds

### 2012-04-19 paper/paper.tex
Update authors

% author names and affiliations
% use a multiple column layout for up to three different
% affiliations
\author{\IEEEauthorblockN{Michael Shell}
  \IEEEauthorblockA{School of Electrical and\\Computer Engineering\\
Georgia Institute of Technology\\
Atlanta, Georgia 30332--0250\\
Email: http://www.michaelshell.org/contact.html}
\and
\IEEEauthorblockN{Homer Simpson}
\IEEEauthorblockA{Twentieth Century Fox\\
Springfield, USA\\
Email: homer@thesimpsons.com}
\and
\IEEEauthorblockN{James Kirk\\ and Montgomery Scott}
\IEEEauthorblockA{Starfleet Academy\\
San Francisco, California 96678-2391\\
Telephone: (800) 555--1212\\
Fax: (888) 555--1212}}

>>>>

% IEE Format
\author{
  \IEEEauthorblockN{Maciej Malawski}
  \IEEEauthorblockA{AGH University of Science and Technology\\
Dept. of Computer Science\\
Krakow, Poland; and\\
University of Notre Dame\\
Center for Research Computing\\
111 ITC, Notre Dame, IN, USA\\
Email: mmalawsk@nd.edu}
  \and
  \IEEEauthorblockN{Gideon Juve and Ewa Deelman}
  \IEEEauthorblockA{USC Information Sciences Institute\\
4676 Admiralty Way\\
Marina del Rey, CA, USA\\
Email: \{gideon,deelman\}@isi.edu}
  \and
  \IEEEauthorblockN{Jarek Nabrzyski}
  \IEEEauthorblockA{University of Notre Dame\\
Center for Research Computing\\
111 ITC, Notre Dame, IN, USA\\
Email: naber@nd.edu}}
